Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-11 man/figures/evi_vs_severe_droughts.Rmd
fix sizes figures

---
output:
  word_document
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

# PLOT EVI + DROUGHT 
combinado2 <- ggplot(evi_profile_dat, aes(cd, y=mean)) + 
  scale_x_date(labels = function(x) format(x, "%b"), breaks = date_breaks('month')) + 
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank()) +
  theme_classic() +
  geom_segment(data = dy, aes(y = mean, x= iD, xend =eD, yend = mean, colour = d_severity), 
               size = 8, alpha = 0.7) +
  geom_text(data = dy, aes(label = year, x = (iD + floor(eD-iD)/2))) +
  scale_colour_gradient(low = "orange", high = "brown") + 
  labs(colour = "Drought Severity") +
  geom_errorbar(aes(ymin = mean - 10*se, ymax= mean + 10*se), width=4, colour=micolor, size=.8) + 
  geom_line(colour=micolor, size=.8) + 
  geom_point(size=3,colour=micolor) +
  geom_point(size=1.5, colour='white') + 
  ylab('EVI') + xlab('')

>>>>

---
output:
  word_document
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

@@

# PLOT EVI + DROUGHT 
combinado2 <- ggplot(evi_profile_dat, aes(cd, y=mean)) + 
  scale_x_date(labels = function(x) format(x, "%b"), breaks = date_breaks('month')) + 
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank()) +
  theme_classic() +
  geom_segment(data = dy, aes(y = mean, x= iD, xend =eD, yend = mean, colour = d_severity), 
               size = 6, alpha = 0.7) +
  geom_text(data = dy, aes(label = year, x = (iD + floor(eD-iD)/2)), size = 3) +
  scale_colour_gradient(low = "orange", high = "brown", 
                        guide = guide_colourbar(direction = "horizontal")) + 
  labs(colour = "Drought \n Severity") +
  geom_errorbar(aes(ymin = mean - 10*se, ymax= mean + 10*se), width=4, colour=micolor, size=.6) + 
  geom_line(colour=micolor, size=.6) + 
  geom_point(size=3,colour=micolor) +
  geom_point(size=1.5, colour='white') + 
  ylab('EVI') + xlab('')

combinado2 <- combinado2 + 
  theme(legend.position = "bottom",
        legend.text=element_text(size=rel(0.8)),
        legend.title =element_text(size=rel(0.8)))

### 2019-04-11 man/figures/ring_climate.Rmd
fix sizes figures

```{r plot_options}
theme_ring_climate <- list(
  geom_hline(yintercept = 0, colour="gray"), 
  geom_bar(aes(fill=site), stat="identity", position = position_dodge2(padding = 0.1)),
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.06))), 
            position = position_dodge(.9), size = 6), 
  theme_bw() +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_line(size=.5),
        axis.text.x.top = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 7),
        axis.text.x.bottom = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 7),
        axis.text.y = element_text(size = 7), 
        axis.title.y = element_text(size = 8),
        legend.text = element_text(size = 7), 
        legend.box.spacing = unit(0.01, "cm")),
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3"), labels = label_site)
) 
```

>>>>

```{r plot_options}
theme_ring_climate <- list(
  geom_hline(yintercept = 0, colour="gray"), 
  geom_bar(aes(fill=site), stat="identity", position = position_dodge2(padding = 0.1)),
  geom_text(aes(label = sig, x = id, y = ifelse(coef > 0, (coef + 0.02), (coef - 0.06))), 
            position = position_dodge(.9), size = 3), 
  theme_bw() +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_line(size=.5),
        axis.text.x.top = element_text(angle = 90, hjust = 0, vjust = 0.5, size = 7),
        axis.text.x.bottom = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 7),
        axis.text.y = element_text(size = 7), 
        axis.title.y = element_text(size = 8),
        legend.text = element_text(size = 7), 
        legend.box.spacing = unit(0.01, "cm")),
  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3"), labels = label_site)
) 
```
